### 2016-10-31 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 3,label = 'B')

@@

temp <- subset(dd,!is.na(Insect))
temp$LogAge <- log(temp$Agemonths)

@@

plot(tapply(dd3$DeltaRTLF,dd3$TimeDiff,mean))

ggplot(dd,aes(col = Whodunnit,y = RTL,x = factor(LayYear)))+
geom_boxplot()

>>>>

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 3,label = 'B')

@@

temp <- subset(dd,!is.na(Insect))
temp$LogAge <- log(temp$Agemonths)
temp$RTL <- log10(temp$RTL)

@@

library(qqman)
?manhattan
